\chapter{Edit Longevity Parameter Rankings}
\label{app:editlong-data}

Presented here is the complete rankings of each parameter
variation explored for the evaluation of edit longevity
presented in Chapter~\ref{ch:editquality}.
In addition to the fields described in Chapter~\ref{ch:editquality},
we also collected some additional measures of the work being
done by the various combinations of parameters.

\textbf{Num Revs} is how many PAN-WVC-10 revisions predictions
were made for.
We would like this to be as high as possible, but WikiTrust will skip
calculating a quality for a revision if it believes the edit distance
from the previous revision is 0; this is because the calculation
includes a division.
In hindsight, it might be better to inspect the edit script directly
to determine when there is no change compare from the previous revision.
When there is no change between revisions, each difference algorithm
will identify a single \textbf{Mov} operation.
This begs the question of how to compute the edit longevity when
the edit distance is zero; a reasonable choice would be setting
the edit longevity to zero when the edit distance is zero.
This choice indicates that there is no bias toward believing that
the revision is either high- or low-quality.

Another measure of work (that is strongly related to the number
of revisions for which predictions are made) is the number of
triangles which are evaluated, \textbf{Total Triangles}, as
illustrated by Figure~\ref{fig-editlong}.
Each side of the triangle is calculated in the computation
for edit longevity (see Eq.~\ref{eq:esurv}).
The column \textbf{Bad Triangles} counts how many of the
triangles evaluated fail to satisfy the triangle inequality.

With respect to the triangle inequality, the data shows that
it is not a necessary property in order to achieve good performance.
In fact, the combination of using a greedy approach to
generating the edit script (which might not generate the
shortest edit script) and our unusual definitions of edit distance
make the triangle inequality an unlikely property.
See~\cite{Sankoff1999} for discussion about when the triangle
inequality might hold, especially in the more difficult case
of including transpositions.
\mynote{especially Sankoff1999, p. 309.  and Chapter 7.}


\input{part-Z20-editquality/quality-table-editlong}

