\section{Introduction}

The Wikipedia is a shared resource of the global community, but it depends on
the continuing participation of volunteers to keep it current and relevant.
Anyone can edit the Wikipedia: this is both its strength and its weakness.
The Wikipedia was initially a side-project of Nupedia, to facilitate collaboration on content
before entering a more formal peer-review process~\cite{wiki:Nupedia}.
The parent project languished in comparison to the Wikipedia because of
this difference in process.  Today, companies such as Facebook have
recognized this strategy and incorporated ``frictionless sharing'' into
their own services.
The price paid by the Wikipedia for this increased participation is the
need to guard against vandalism.
Multiple studies have found that roughly 7\% of edits are
vandalism~\cite{Potthast2008,Potthast2010a}.
To combat the vandalism, a group of volunteers scan the list of recent changes
to catch obvious damage quickly~\cite{wiki:RCPatrol}.

In the chapters leading to this one, we have detailed the technologies
necessary to build a content-driven reputation system for authors.
We first constructed a difference algorithm to compute the work done in a
revision, doing so in a way which models how users think about the units of
language, while maintaining performance such that the entire English Wikipedia
could be evaluated in a tractable amount of time.
We then proposed two methods for evaluating the quality of the work done by the
users in their revisioning: text longevity and edit longevity.
Finally, we use these quality measures as the basis for rules in a reputation
system.
The output of this reputation system is an estimate of the balance of past
positive contributions over past negative contributions, which we evaluate
as a predictor of the future quality of revisions by the same author.

As part of the PAN 2010 Workshop on vandalism
detection\footnote{\url{http://www.webis.de/research/events/pan-10}, Task 2},
a competition was organized to test vandalism detection systems with a
single evaluation measure.
Our research group submitted a system based on features derived from
WikiTrust~\cite{Adler2010b}, leaving out the actual reputation scores due
to our lack of historical reputation values for authors.
In this chapter, we revisit that work and update it by including
the reputation score of authors at the time of their edits.

