\clearpage

\vfill
\vskip5in

\begin{center}
\textit{
To Pokey and Lala, \\
who both taught me what I really needed to learn.
}
\end{center}

\vspace{1in}

\begin{center}
\Heart\quad\Heart\quad\Heart
\end{center}


\vfill

\clearpage

\chapter{Acknowledgements}

Thanks to Luca, who never gave up when I needed him and stuck with
me through the ups and downs of the years.
And to my labmates and co-authors, Marco, Vishwa, Ian, Pritam, Leandro, Krish,
and Axel: your moral (and research) support
was invaluable at so many points for keeping me engaged.
I learned a great deal and appreciate all that you shared
with me.  And finally, Karen deserves a special thanks as one of the few
people to read through this whole document.

There are a few heroes that saw me through the darkest hours;
I am indebted to you for your caring when mine failed me.
And there are so many friends and family, new and old,
that were characters in this adventure and gave me their
support and encouragement and compassion.
You all have my deepest thanks.


%I had no idea there was so much dancing involved in grad school.

\vskip.25in
\begin{center}
I am the luckiest one.
\end{center}

\vfill

The text of this dissertation includes excerpts of
previously published material; copyright of this material
remains with its respective holders and appears here with their permission.
Chapters~\ref{ch:diff}, \ref{ch:editquality}, and~\ref{ch:reputation}
expand on the initial paper presenting our content-driven reputation
ideas for the Wikipedia~\cite{Adler2007}.
Chapter~\ref{ch:contrib} is a reprint of our investigation into
contribution measures~\cite{Adler2008a}.
Chapter~\ref{ch:vandalism} covers similar ground as (and includes
some material from) two previously
published works~\cite{Adler2010b,Adler2011a}.

This work was supported in part by the Center for Information
Technology Research in the Interest of Society (CITRIS), and
by the Institute for Scalable Scientific Data Management (ISSDM).


