%\documentclass{acm_proc_article-sp}
\documentclass{sig-alternate}
\usepackage{latexsym,amssymb,amsmath}
\usepackage{epic,eepic}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{url}
%\usepackage{hyperref}
%\usepackage{breakurl}
\setlength{\columnsep}{0.7cm}
\usepackage{macro,luca}
\usepackage{times}

\begin{comment}
\hypersetup{
%    bookmarks=true,         % show bookmarks bar?
%    unicode=false,          % non-Latin characters in Acrobat's bookmarks
%    pdftoolbar=true,        % show Acrobat's toolbar?
%    pdfmenubar=true,        % show Acrobat's menu?
    pdffitwindow=true,      % page fit to window when opened
    pdftitle={Measuring Author Contributions to the Wikipedia},    % title
    pdfauthor={B. Thomas Adler, Luca de Alfaro, Ian Pye, Vishwanath Raman},     % author
    pdfsubject={Wikipedia Contributions},   % subject of the document
    pdfnewwindow=true,      % links in new window
%    pdfkeywords={keywords}, % list of keywords
    colorlinks=false,       % false: boxed links; true: colored links
    linkcolor=black,          % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=black,      % color of file links
    urlcolor=blue,           % color of external links
    breaklinks=true
}
\end{comment}

\conferenceinfo{WikiSym '08,}{September 8--10, Porto, Portugal.}
\CopyrightYear{2008}
\crdata{978-1-60558-128-3/08/09}

\begin{document}
\sloppy

\newif
  \iflong
  \longfalse
\newif
  \ifshort
  \shorttrue

\pagestyle{plain}

\title{Measuring Author Contributions to the Wikipedia\titlenote{This 
    research has been
    partially supported by the CITRIS: Center for Information
    Technology Research in the Interest of Society.\\
    Copyright ACM, 2008.  This is the authors' version of the work.
    It is posted here by permission of the ACM for your personal use.
    Not for redistribution.  The definitive version was published in 
    Proceedings of WikiSym 2008.
    \vspace*{-5mm}
  }}

\numberofauthors{4}
\author{
B. Thomas Adler$^1$ \qquad
Luca de Alfaro$^2$ \qquad
Ian Pye$^1$ \qquad
Vishwanath Raman$^1$
\and
\alignauthor
	\affaddr{$^1$Computer Science Dept.} \\
	\affaddr{UC Santa Cruz, CA, USA} \\
	\email{\{thumper, vishwa, ipye\}@soe.ucsc.edu}
\alignauthor
	\affaddr{$^2$Computer Engineering Dept.} \\
	\affaddr{UC Santa Cruz, CA, USA} \\
	\email{luca@soe.ucsc.edu}
}

\maketitle

\begin{abstract}
\input{abstract}
\end{abstract}

% A category with the (minimum) three required fields
\category{H.5.3}{Information Interfaces and Presentation}{Group
and Organization Interfaces}[Computer-supported cooperative work, 
Web-based interaction]
\category{K.4.3}{Computers and Society}{Organizational Impacts}
[Computer-supported collaborative work]
%A category including the fourth, optional field follows...
\category{J.4}{Social and Behavioral Sciences}{Miscellaneous}

\pagebreak
\input{introduction}
\input{definitions}
\input{contributions}
\input{implementation}
\input{analysis}
\input{conclusion}

% \bibliographystyle{plain}
% \bibliography{dvlab}

\begin{thebibliography}{10}

\bibitem{trust-techrep-07}
B.T. Adler, J.~Benterou, K.~Chatterjee, L.~de~Alfaro, I.~Pye, and V.~Raman.
\newblock Assigning trust to wikipedia content.
\newblock Technical Report UCSC-CRL-07-09, School of Engineering, University of
  California, Santa Cruz, CA, USA, 2007.

\bibitem{www07}
B.T. Adler and L.~de~Alfaro.
\newblock A content-driven reputation system for the {Wikipedia}.
\newblock In {\em Proc. of the 16th Intl. World Wide Web Conf. (WWW 2007)}.
  {ACM} Press, 2007.

\bibitem{AdministratorMop2008}
M.~Burke and R.~Kraut.
\newblock Taking up the mop: identifying future {W}ikipedia administrators.
\newblock In {\em CHI '08: CHI '08 extended abstracts on Human factors in
  computing systems}, pages 3441--3446, New York, NY, USA, 2008. ACM.

\bibitem{EditDistanceMoves}
G.~Cormode and S.~Muthukrishnan.
\newblock The string edit distance matching problem with moves.
\newblock {\em ACM Trans. Algorithms}, 3(1):2, 2007.

\bibitem{Wikis01}
W.~Cunningham and B.~Leuf.
\newblock {\em The Wiki Way. {Quick} Collaboration on the Web}.
\newblock Addison-Wesley, 2001.

\bibitem{SLOC1992}
R.~E.~Park et~al.
\newblock Software size measurement: A framework for counting source
  statements.
\newblock Technical Report CMU/SEI-92-TR-020, Carnegie Mellon University,
  September 1992.

\bibitem{AckCounting2004}
C.~L. Giles and I.~G. Councill.
\newblock Who gets acknowledged: Measuring scientific contributions through
  automatic acknowledgement indexing.
\newblock {\em Proc. of the National Academy of Sciences}, 101(51):17599 --
  17604, 2004.

\bibitem{Bourgeoisie2007}
A.~Kittur, E.~Chi, B.~A. Pendleton, B.~Suh, and T.~Mytkowicz.
\newblock Power of the {F}ew vs. {W}isdom of the {C}rowd: {W}ikipedia and the
  rise of the {B}ourgeoisie.
\newblock {\em Alt.CHI}, 2007.

\bibitem{KPB2006}
N.~Korfiatis, M.~Poulos, and G.~Bokos.
\newblock Evaluating authoritative source using social networks: an insight
  from {W}ikipedia.
\newblock {\em Online Information Review}, 30(3):252--262, 2006.

\bibitem{Levenshtein66}
V.I. Levenshtein.
\newblock Binary codes capable of correcting insertions and reversals.
\newblock {\em Sov.\ Phys.\ Dokl.}, 10:707--710, 1966.

\bibitem{WikiMTWtrust06}
D.L. McGuinness, H.~Zeng, P.P. da~Silva, L.~Ding, D.~Narayanan, and M.~Bhaowal.
\newblock Investigation into trust for collaborative information repositories:
  {A} {Wikipedia} case study.
\newblock In {\em Proceedings of the Workshop on Models of Trust for the Web},
  2006.

\bibitem{OrtegaBarahona2007}
F.~Ortega and J.~M.~G. Barahona.
\newblock Quantitative analysis of the {W}ikipedia community of users.
\newblock In {\em WikiSym '07: Proceedings of the 2007 international symposium
  on Wikis}, pages 75--86, New York, NY, USA, 2007. ACM.

\bibitem{PageRank98}
L.~Page, S.~Brin, R.~Motwani, and T.~Winograd.
\newblock The {PageRank} citation ranking: Bringing order to the web.
\newblock Technical report, Stanford Digital Library Technologies Project,
  1998.

\bibitem{R2007}
{R Development Core Team}.
\newblock {\em R: A Language and Environment for Statistical Computing}.
\newblock R Foundation for Statistical Computing, Vienna, Austria, 2007.
\newblock {ISBN} 3-900051-07-0.

\bibitem{MITRE1988}
H.~P. Schultz.
\newblock Software management metrics.
\newblock Technical Report AD-A196 916, MITRE, May 1988.

\bibitem{CognitiveSurplus2008}
C.~Shirky.
\newblock Gin, television, and social surplus.
\newblock
  \url{http://www.herecomeseverybody.org/2008/04/looking-for-the-mouse.html},
  April 2008.
\newblock (Retrieved on 9-May-2008.).

\bibitem{SteinHess2007}
K.~Stein and C.~Hess.
\newblock Does it matter who contributes: a study on featured articles in the
  german wikipedia.
\newblock In {\em HT '07: Proceedings of the 18th conference on Hypertext and
  hypermedia}, pages 171--174, New York, NY, USA, 2007. ACM.

\bibitem{WikiDashboard2008}
B.~Suh, E.~H. Chi, A.~Kittur, and B.~A. Pendleton.
\newblock Lifting the veil: improving accountability and social transparency in
  {W}ikipedia with wikidashboard.
\newblock In {\em CHI '08: Proceeding of the twenty-sixth annual SIGCHI
  conference on Human factors in computing systems}, pages 1037--1040, New
  York, NY, USA, 2008. ACM.

\bibitem{Swartz2006}
A.~Swartz.
\newblock Who writes {W}ikipedia?
\newblock \url{http://www.aaronsw.com/weblog/whowriteswikipedia}, September
  2006.
\newblock (Retrieved on 9-May-2008.).

\bibitem{TichyEditDist}
W.F. Tichy.
\newblock The string-to-string correction problem with block move.
\newblock {\em {ACM} Trans.\ on Computer Systems}, 2(4), 1984.

\bibitem{Voss2005}
J.~Vo\ss{}.
\newblock Measuring wikipedia.
\newblock In {\em Proc.\ of the 10th Intl.\ Conf.\ of the ISSI}, 2005.

\bibitem{EditDist74}
Robert~A. Wagner and Michael~J. Fischer.
\newblock The string-to-string correction problem.
\newblock {\em J. ACM}, 21(1):168--173, 1974.

\bibitem{Wales2005}
J.~Wales.
\newblock Wikipedia, emergence, and the wisdom of crowds.
\newblock
  \url{http://lists.wikimedia.org/pipermail/wikipedia-l/2005-May/021764.html},
  May 2005.
\newblock (Retrieved 9-May-2008.).

\bibitem{EditsEqQuality2007}
D.~M. Wilkinson and B.~A. Huberman.
\newblock Cooperation and quality in wikipedia.
\newblock In {\em WikiSym '07: Proceedings of the 2007 international symposium
  on Wikis}, pages 157--164, New York, NY, USA, 2007. ACM.

\end{thebibliography}

\end{document}
